% Resume in LaTeX
% Author: Nutthawat Panyangnoi

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{fontawesome5}

% Adjust margins
\addtolength{\oddsidemargin}{-0.8in}
\addtolength{\evensidemargin}{-0.4in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.5in}

% Section formatting
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\normalsize\bfseries}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Compact item list spacing
\setlist[itemize]{leftmargin=*, itemsep=1pt, parsep=0pt, topsep=0pt}

% Ensure PDF is machine-readable
\pdfgentounicode=1

\begin{document}
\vspace{-10pt}
\begin{center}
    {\Large \textbf{NUTTHAWAT PANYANGNOI}} \vspace{1pt} \\
    \small 
    \faPhone\ (209) 407-9730 ~|~
    \href{mailto:panyangnoi.nutthawat@gmail.com}{\faEnvelope\ panyangnoi.nutthawat@gmail.com} ~|~
    \href{https://www.linkedin.com/in/nathan-panyangnoi/}{\faLinkedin\ linkedin.com/in/nathan-panyangnoi/} \\
    \href{https://github.com/kur0neko}{\faGithub\ github.com/kur0neko}
\end{center}

%-----------EDUCATION-----------
%\section{Education}
%\begin{itemize}
%   \item \textbf{San Jose State University}, San Jose, CA \hfill \textbf{Dec 2025} \\ 
%  \textbf{B.S. Computer Engineering}, Minor: Computer Science ~|~ GPA: 3.35/4.0 \\
% \item \textbf{Las Positas College}, Livermore, CA \hfill \textbf{May 2022} \\
%\textbf{A.S. Computer Science}, Minor: Math ~|~ GPA: 3.5/4.0 \\
% \item \textbf{King Mongkut’s University of Technology Thonburi}, Bangkok, Thailand \hfill \textbf{May 2013} \\ 
% \textbf{B.S. Computer Science} (75 credits completed; transferred due to family relocation to California)
%\end{itemize}

\section{EDUCATION}
\begin{itemize}
    \item \textbf{San Jose State University}, San Jose, CA \hfill \textbf{Dec 2025} \\ 
    \textbf{B.S. Computer Engineering}, Minor: Computer Science ~|~ GPA: 3.35/4.0 
    \item \textbf{Las Positas College}, Livermore, CA \hfill \textbf{May 2022} \\
    \textbf{A.S. Computer Science}, Minor: Math ~|~ GPA: 3.5/4.0 
\end{itemize}
%------RELEVANT COURSEWORK-------
%\section{Relevant Coursework}
%\begin{itemize}
%    \item Software Engineering, Digital Circuits, Data Structures
%    \item Embedded Systems, OS Design, Computer Architecture, Compiler Design, Networks
%    \item Assembly, Databases (SQL/NoSQL), OOD/OOP C/C++, Java, Python, Verilog
%\end{itemize}
%-----------TECHNICAL SKILLS-----------
%\section{TECHNICAL SKILLS}
%\begin{itemize}
%    \item \textbf{Programming Languages:} C, C++, Python, JavaScript, React Native, React, SQL, Verilog, HTML, CSS
%    \item \textbf{Software:} VMware, Docker, Office 365, SolidWorks, LTspice, Vivado, Figma UI design and diagrams(UML,Block) 
%    \item \textbf{Networking:} TCP/IP, DNS/DHCP, NAS Setup, VPN Configuration
%    \item \textbf{Hardware:} IT Support, Computer Assembly (NASM, MASM), Server Setup, Troubleshooting, BIOS Flashing, RAID Configuration, Oscilloscope
%    \item \textbf{Operating Systems:} Windows, Linux (Mint, Arch, Ubuntu), macOS
%\end{itemize}
\section{TECHNICAL SKILLS}
\begin{itemize}
    \item \textbf{Programming Languages:} C, C++, Python, JavaScript, SQL, Verilog, HTML, CSS, (Familiar with C#)
    \item \textbf{Deep Learning / ML:} PyTorch, TensorFlow, NumPy, Scikit-learn, OpenCV, Jupyter
    \item \textbf{Embedded Systems:} Raspberry Pi CM4, NVIDIA Jetson (familiar), FPGA (Verilog/SystemVerilog), LTspice, Oscilloscope, KiCad
    \item \textbf{Software:} Docker, VMware, Vivado, SolidWorks, Office 365, Figma
    \item \textbf{Hardware:} IT Support, BIOS Flashing, RAID, VPN, NAS, Troubleshooting
    \item \textbf{Operating Systems:} Linux (Ubuntu, Arch, Mint), Windows, macOS
\end{itemize}
%-----------WORK EXPERIENCE-----------
\section{WORK EXPERIENCE}
\textbf{NASA MSFC NPWEE Program} — \textit{Electrical \& Computer Engineer }\hfill \textbf{Aug 2024 -- Dec 2024} \\
\textit{Remote}
\begin{itemize}
    \item Conducted technical research on high-voltage battery tech for space missions, enabling compact energy systems with potential for laser charging integration.
    \item Collaborated on systems-level algorithm design for battery efficiency modeling and embedded energy control logic.
    \item Pitched and co-authored an innovation proposal selected by NASA MSFC for further development.
\end{itemize}
\textbf{NASA MCA by NASA MSFC} — \textit{Program Analyst \&  Computer Hardware Engineer} \hfill \textbf{Jan 2024 -- Aug 2024} \\
\textit{Remote}
\begin{itemize}
    \item Collaborated with a team of engineering students on a simulated NASA Discovery Mission to design and execute a lunar water sample collection operation.
    \item Managed financial and resource planning to ensure mission feasibility, including cost estimation and analysis for the Preliminary Design Review (PDR). 
    \item Conducted mission cost estimation, resource analysis, and project timeline forecasting for major design milestones (MCR, SRR, MDR) using NASA tools such as NICM CERs/SERs and MCCET
\end{itemize}
\textbf{Mountain Cascade, Inc.} — \textit{IT Technician (Full-time)} \hfill \textbf{Mar 2020 -- Aug 2023} \\
\textit{Livermore, CA}
\begin{itemize}
    \item Provided comprehensive IT support, diagnosing hardware and software issues in a Windows environment.
    \item Performed hands-on BIOS flashing, RAID setup, VPN configuration, NAS configuration and server maintenance.
    \item Provided hands-on support includes break/fix, service request fulfillment, deployments, upgrades, and hardware lifecycle management.
\end{itemize}
\textbf{Amber System Technology} — \textit{Frontend Software Developer} \hfill \textbf{Apr 2018 -- Mar 2020} \\
\textit{Pleasanton, CA}
\begin{itemize}
    \item Designed and implemented POS UI/UX for customer specific need to help them operate business better.
    \item Led frontend feature development ensuring align with customer requirements and business goals.
    \item Developed full stack website solutions to meet client-specific requirements using React, nodeJS,and MongoDB,
\end{itemize}
\textbf{Volcano Splash Drinks (Family Business)} — \textit{Barista, Manager, Business Owner} \hfill \textbf{Aug 2013 -- Dec 2018} \\
\textit{Tracy, Stockton, Pleasanton, San Jose CA}
\begin{itemize}
    \item Partnered with SPECTRA by Comcast Spectacor to provide beverage services; coffee, smoothies, at baseball stadiums and public events.
    \item Operated in various roles, including customer service, management, and marketing for a family-owned business.
    \item Managed seasonal staffs over 60 people and led day-to-day operations of concession stands, ensuring high-quality service delivery during events.
\end{itemize}
%-----------PROJECTS-----------
\section{PROJECTS}
\textbf{FoodReal iOS Application} \textit{(React Native, Tailwind, Expo, Firebase)} \hfill \textbf{In Progress} 
\begin{itemize}
    \item Developing a mobile app that encourages users to cook at home and share meals on social media to inspire others.
    \item Designed an intuitive, swipe-based interface with a user-friendly UI for seamless engagement.
\end{itemize}
\textbf{Handheld Computing Device} \textit{(C, C++, Linux, KiCad, LTspice, Raspberry Pi CM4)} \hfill \textbf{In Progress} 
\begin{itemize}
    \item Engineered a modular computing system using the Raspberry Pi CM4, ClockworkPi v3.14 mainboard, and battery module.
    \item Built a custom Linux-based OS from scratch, including bootloader setup, device tree configuration, and filesystem optimization.
\end{itemize}
\textbf{Note Hub Web Application} \textit{(Python, Flask, SQLAlchemy, Django)} \hfill \textbf{Jan 2023 -- Apr 2023} 
\begin{itemize}
    \item Created a Notion-inspired web app with Flask and SQLite for note-taking and organization.
    \item Implemented secure user authentication using session-based login management.
\end{itemize}
\textbf{Neural Network Deployment} \textit{(PyTorch, Python, Raspberry Pi)} \hfill \textbf{Apr 2025 -- May 2025} 
\begin{itemize}
    \item Trained convolutional neural networks (CNNs) on a sign language image dataset and deployed the model to a Raspberry Pi with integrated webcam.
    \item Optimized inference using PyTorch quantization and evaluated hardware performance based on latency and accuracy benchmarks.
\end{itemize}
\textbf{Waveform Generator Circuit Design / DC-to-AC Converter} \textit{(LTspice, Breadboard)} \hfill \textbf{Jan 2023 -- Apr 2023}
\begin{itemize}
    \item Designed and simulated a square/triangle waveform generator using CD-40106 and BC547B components in LTspice.
    \item Constructed the circuit on a breadboard and validated waveform outputs using an oscilloscope.
\end{itemize}


%-----------CERTIFICATIONS-----------
\section{CERTIFICATIONS}
\textbf{NASA L’Space Mission Concept Academy} \hfill \textbf{Aug 2024}
\begin{itemize}
    \item Earned certification after completing a 3.5-month program focused on a simulated NASA Discovery mission, culminating in the Preliminary Design Review (PDR), under the guidance of NASA Marshall Space Flight Center (MSFC).
\end{itemize}
\textbf{NASA Proposal Writing \& Evaluation Experience} \hfill \textbf{Dec 2024}
\begin{itemize}
    \item Earned certification after a 3.5-month collaboration on a space innovation proposal, co-authoring the development of high-voltage, laser-chargeable battery technology with greater power density and lower weight than conventional lithium-ion cells.
\end{itemize}


\end{document}
